---
title: "R Notebook"
output: html_notebook
---

```{r}
<<<<<<< HEAD
library(readr)
library(stringr)
library(data.table)
library(dataplumbr)


col_delim <- "|"
#col_num <- 145
#col_delim_num <- col_num - 1
file_path <- "/project/biocomplexity/sdad/projects_data/usda/bb/original/Corelogic_June_2020_Files/Corelogic_USDA_Current_Tax_2020_06_27.txt"
first_line <- readLines(file_path, n = 1)
col_delim_num <- stringr::str_count(first_line, "\\|")
col_num <- col_delim_num + 1

db_schema_name <- "corelogic_usda"
db_table_name <- tolower("Corelogic_USDA_Current_Tax_2020_06_27")
db_col_names <- dataplumbr::name.standard_col_names(stringr::str_split(first_line, "\\|")[[1]]) %>% 
  stringr::str_replace("^_", "") %>% 
  stringr::str_replace("_$", "")

db_col_names <- db_col_names[1:188]


dt <- data.table(V1="")
for (n in db_col_names) {
  dt[, eval(n) := ""]  
}
dt[, V1 := NULL]


=======

col_delim <- "|"
col_num <- 145
col_delim_num <- col_num - 1
file_path <- "/project/biocomplexity/sdad/projects_data/usda/bb/original/corelogic/8state/TaxHistory.Tax_History_05.csv"
>>>>>>> 9a3e96ca8813b4656a11e8aa2ee467c6674cd943
file_ext <- tools::file_ext(file_path)
file_path_no_ext <- tools::file_path_sans_ext(file_path)
cut_col_path <- paste0(file_path_no_ext, "_", col_num,"cols.", file_ext)
ascii_path <- paste0(tools::file_path_sans_ext(cut_col_path), "_ascii.", file_ext)
no_quote_path <- paste0(tools::file_path_sans_ext(ascii_path), "_noqt.", file_ext)

Sys.setenv(col_delim=col_delim)  
Sys.setenv(col_num=col_num)
Sys.setenv(col_delim_num=col_delim_num)
Sys.setenv(file_path=file_path)
Sys.setenv(cut_col_path=cut_col_path)
Sys.setenv(ascii_path=ascii_path)
Sys.setenv(no_quote_path=no_quote_path)
<<<<<<< HEAD
Sys.setenv(db_schema_name=db_schema_name)
Sys.setenv(db_table_name=db_table_name)
=======
>>>>>>> 9a3e96ca8813b4656a11e8aa2ee467c6674cd943
Sys.setenv(PGUSER=Sys.getenv("db_usr"))
Sys.setenv(PGPASSWORD=Sys.getenv("db_pwd"))

```

<<<<<<< HEAD
```{bash}
# select columns
cut -d "$col_delim" -f 1-188 $file_path > $cut_col_path

=======

```{bash}
# select columns
cut -d "$col_delim" -f 1-$col_num $file_path > $cut_col_path
>>>>>>> 9a3e96ca8813b4656a11e8aa2ee467c6674cd943
```

```{bash}
# remove non-ascii
tr -cd '\11\12\15\40-\176' < $cut_col_path > $ascii_path
<<<<<<< HEAD
#tr -cd '\11\12\15\40-\176' < $file_path > $ascii_path
```

```{bash}
# sed 's/\"//g' < $ascii_path > $no_quote_path
sed 's/\"//g' < $file_path > $no_quote_path
```

```{bash}
echo '"34013"|"0200362000000011"|"02-00362-0000-00011"|"1"|""|"Y"|"TRD REALTY LLC"|""|""|"LOLOS"|"RALPH"|"1"|""|""|""|""|""|"40.781789"|"-74.190544"|""|""|""|""|"BLOOMFIELD"|"AVE"|""|""|"BLOOMFIELD"|"NJ"|"070035621"|"C026"|""|""|""|""|""|""|""|""|""|""|""|""|"20081120"|"90"|"Y"|""|""|"METRO FNDG"|""|""|""|""|"20081003"|"LP"|""|"8090908"|"012160009386"|""|""|""|""|""|""|""|""|"ATTORNEY ONLY"|"00400"|"300000.00"|"20080521"|""|""|""|""|""|""|""|""|"F"|""|""|""|"200"|"20"|""|"False"|"0"|""|"0"|""|""|""|""|""|""|""|""|"200000"|"169900"|"30100"|"10900.00"|"2007"|"2008"|""|""|".3100"|"13503.6000"|""|""|""|"1922"|""|""|""' | sed 's/\"//g'
```
```{bash}
echo '"34013"|"0200362000000011"|"02-00362-0000-00011"|"1"|""|"Y"|"TRD REALTY LLC"|""|""|"LOLOS"|"RALPH"|"1"|""|""|""|""|""|"40.781789"|"-74.190544"|""|""|""|""|"BLOOMFIELD"|"AVE"|""|""|"BLOOMFIELD"|"NJ"|"070035621"|"C026"|""|""|""|""|""|""|""|""|""|""|""|""|"20081120"|"90"|"Y"|""|""|"METRO FNDG"|""|""|""|""|"20081003"|"LP"|""|"8090908"|"012160009386"|""|""|""|""|""|""|""|""|"ATTORNEY ONLY"|"00400"|"300000.00"|"20080521"|""|""|""|""|""|""|""|""|"F"|""|""|""|"200"|"20"|""|"False"|"0"|""|"0"|""|""|""|""|""|""|""|""|"200000"|"169900"|"30100"|"10900.00"|"2007"|"2008"|""|""|".3100"|"13503.6000"|""|""|""|"1922"|""|""|""' | tr -cd '\11\12\15\40-\176' | sed 's/\"//g'
```


=======
```

```{bash}
sed 's/\"//g' < $ascii_path > $no_quote_path
```

>>>>>>> 9a3e96ca8813b4656a11e8aa2ee467c6674cd943
```{bash}
# validate number of delimiters
#echo $col_delim'\n'
tr -cd $col_delim'\n' < $no_quote_path | awk 'length!='$col_delim_num' {print NR}'
```

<<<<<<< HEAD
```{r}
source("db_connection.R")
con <- get_db_conn()
DBI::dbWriteTable(con, c(db_schema_name, db_table_name), dt, overwrite=T, row.names=F)
DBI::dbDisconnect(con)
```


```{bash}
# create copy command for upload
# upload NO QUOTE
echo "psql -U $PGUSER -h postgis1 -d sdad -c \"\copy $db_schema_name.$db_table_name from $no_quote_path WITH (FORMAT 'csv', DELIMITER E'\|', QUOTE E'\b', HEADER);\""
=======
```{bash}
# create copy command for upload
# upload NO QUOTE
echo "psql -U $PGUSER -h postgis1 -d sdad -c \"\copy corelogic_usda.tax_hist_05 from $no_quote_path WITH (FORMAT 'csv', DELIMITER E'\|', QUOTE E'\b', HEADER);\""
>>>>>>> 9a3e96ca8813b4656a11e8aa2ee467c6674cd943
```


```{bash}
# create trigram indexes
#for (i in c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10")) {
#  sql <- paste0("CREATE INDEX corelogic_sdad_tax_hist_", i, "_fips_code_trgm_idx ON corelogic_sdad.tax_hist_", i, " USING GIST (fips_code gist_trgm_ops);")
#}
col="fips_code"
for i in 01 02 03 04 05 06 07 08 09 10
do
	sql="CREATE INDEX corelogic_sdad_tax_hist_"$i"_fips_code_trgm_idx ON corelogic_sdad.tax_hist_"$i" USING GIST ("$col" gist_trgm_ops);"
	echo $sql
done
```



# BUILD STATE TABLES
```{r}
source("db_connection.R")
con <- get_db_conn()
sql <- "select \"STATEFP\" fips_code_st, lower(\"STUSPS\") abbrev, \"NAME\" st_name from gis_census_cb.cb_2018_us_state_500k;"
state_codes <- DBI::dbGetQuery(con, sql)
DBI::dbDisconnect(con)

#for (i in 1:nrow(state_codes)) {
for (i in 46:56) {
  fips_code_st <- state_codes[i,]$fips_code_st
  abbrev <- state_codes[i,]$abbrev
  table_name <- paste0("corelogic_prop_tax_2003_2019.", abbrev, "_pl_prop_tax")
  
  con <- get_db_conn()
  sql <- paste0("select * into ", table_name, " from (
                  select * from corelogic_sdad.tax_hist_01 where fips_code like '", fips_code_st,"%'
                  union all
                  select * from corelogic_sdad.tax_hist_02 where fips_code like '", fips_code_st,"%'
                  union all
                  select * from corelogic_sdad.tax_hist_03 where fips_code like '", fips_code_st,"%'
                  union all
                  select * from corelogic_sdad.tax_hist_04 where fips_code like '", fips_code_st,"%'
                  union all
                  select * from corelogic_sdad.tax_hist_05 where fips_code like '", fips_code_st,"%'
                  union all
                  select * from corelogic_sdad.tax_hist_06 where fips_code like '", fips_code_st,"%'
                  union all
                  select * from corelogic_sdad.tax_hist_07 where fips_code like '", fips_code_st,"%'
                  union all
                  select * from corelogic_sdad.tax_hist_08 where fips_code like '", fips_code_st,"%'
                  union all
                  select * from corelogic_sdad.tax_hist_09 where fips_code like '", fips_code_st,"%'
                  union all
                  select * from corelogic_sdad.tax_hist_10 where fips_code like '", fips_code_st,"%'
                ) t")
  #print(sql)
  DBI::dbGetQuery(con, sql)
  DBI::dbDisconnect(con)
}

```

```{r}
source("db_connection.R")
con <- get_db_conn()
sql <- "SELECT table_name FROM information_schema.tables WHERE table_schema = 'corelogic_prop_tax_2003_2019'"
table_names <- DBI::dbGetQuery(con, sql)
DBI::dbDisconnect(con)

for (i in 1:nrow(table_names)) {
  table_name <- table_names[i,]
  
  con <- get_db_conn()
  sql <- paste0("SELECT                             
                    tablename,
                    indexname,
                    indexdef
                FROM
                    pg_indexes
                WHERE
                    tablename = '", table_name,"' 
                ORDER BY
                    tablename,
                    indexname;")
  idx <- DBI::dbGetQuery(con, sql)
  if (nrow(idx) == 0) {
    sql <- paste0("CREATE INDEX ", table_name,"_tax_year_idx ON corelogic_prop_tax_2003_2019.", table_name," (tax_year);")
    print(paste("creating index on table", table_name))
    DBI::dbGetQuery(con, sql)
  }
  DBI::dbDisconnect(con)
}

<<<<<<< HEAD
```

```{r}
source("db_connection.R")
con <- get_db_conn()
sql <- "SELECT table_name FROM information_schema.tables WHERE table_schema = 'corelogic_prop_tax_2003_2019'"
table_names <- DBI::dbGetQuery(con, sql)
DBI::dbDisconnect(con)

for (i in 1:nrow(table_names)) {
  table_name <- table_names[i,]
  
  con <- get_db_conn()
  sql <- paste0("SELECT                             
                    tablename,
                    indexname,
                    indexdef
                FROM
                    pg_indexes
                WHERE
                    tablename = '", table_name,"'
                AND
                    indexname LIKE '%census_tract%'
                ORDER BY
                    tablename,
                    indexname;")
  idx <- DBI::dbGetQuery(con, sql)
  
  if (nrow(idx) == 0) {
    sql <- paste0("CREATE INDEX ", table_name,"_census_tract_idx ON corelogic_prop_tax_2003_2019.", table_name," USING GIST (census_tract gist_trgm_ops);")
    print(paste("creating index on table", table_name))
    DBI::dbGetQuery(con, sql)
  }
  DBI::dbDisconnect(con)
}

```

```{r}
source("db_connection.R")
con <- get_db_conn()
sql <- "SELECT table_name FROM information_schema.tables WHERE table_schema = 'corelogic_prop_tax_2003_2019'"
table_names <- DBI::dbGetQuery(con, sql)
DBI::dbDisconnect(con)

for (i in 1:nrow(table_names)) {
  table_name <- table_names[i,]
  
  con <- get_db_conn()
  sql <- paste0("SELECT                             
                    tablename,
                    indexname,
                    indexdef
                FROM
                    pg_indexes
                WHERE
                    tablename = '", table_name,"'
                AND
                    indexname LIKE '%fips_code%'
                ORDER BY
                    tablename,
                    indexname;")
  idx <- DBI::dbGetQuery(con, sql)
  
  if (nrow(idx) == 0) {
    sql <- paste0("CREATE INDEX ", table_name,"_fips_code_idx ON corelogic_prop_tax_2003_2019.", table_name," (fips_code);")
    print(paste("creating index on table", table_name))
    DBI::dbGetQuery(con, sql)
  }
  DBI::dbDisconnect(con)
}

=======
>>>>>>> 9a3e96ca8813b4656a11e8aa2ee467c6674cd943
```